%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Rahmat Wahyu Hadi -- Resume} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Kebon Kacang 41,\\ % Address line 1
\> Tanah Aabang , Jakarta Pusat  \\ % Address line 2
{\bf Date of Birth} \> 30$^{th}$ Agust 1995 \\ % Date of birth 
{\bf Nationality} \> Indonesia % Nationalitys
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +62 85205039835 \\ % Home phone
{\bf Github} \> https://github.com/wahyuhadi\\ % Mobile phone
{\bf Email} \> \href{mailto:hrahmatwahyu@gmail.com}{hrahmatwahyu@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

I'm a software developer , mainly working on High level software developments, quite adept to Linux development. 
I've been using Python and Go-lang as my programming language for about 5 years. My driver development experiences are still limited to Linux OS,  I'm back trying to catch-up with the rest of the industry in those subjects. Over the years, I've been working on  Security Engineer as well.


\section{Employment History}

\job
{April 2019 -}{Present}
{PT. Global Tiket Network, Gedung Graha Niaga Thamrin, Kota Jakarta Pusat 12980}
{https://www.tiket.com/}
{Senior Security Engineer - Red Team and Automation (tiket.com)}
{
    \begin{itemize-noindent}

        \item{Perform security code review.} 
        \item{Analyzes and recommends security controls and procedures in acquisition.}
        \item{Development, and change management lifecycle of information systems.}
        \item{Monitors information systems for security incidents and vulnerabilities.}
        \item{Maintains and operates information system security controls and countermeasures.}
        \item{Perform regular penetration testing as well as provide the guidelines for mitigation.}
        \item{Maintenance security bug with relevant development teams for fixes.}
        \item{Develop User Access Matrix for monitoring Access and Credential (uam)}
        \item{Participate in security assessments and compliance such as PCI DSS, ISO 27001, OWASP.}
        \item{Deliver security awareness to Tiket new employees in terms of following compliances}
        \item{Develop Github Monitoring to prevent code and credential leaks in public (gitmon)}
    \end{itemize-noindent}

}
%------------------------------------------------

\job
{Agust 2017 -}{April 2019}
{PT Gits Indonesia.  Margacinta No.29, Cijaura, Kec. Buahbatu, Kota Bandung, Jawa Barat 40287}
{https://gits.co.id/}
{Backend Engineer and Code Review}
{

    \begin{itemize-noindent}
        \item{Develop new Nodejs Framework for developers.}
        \item{Gather specifications and requirements based on clients needs.}
        \item{Develop application based on client requirement.}
        \item{Perform testing to ensure the system has been ready to release version.}
        \item{Implementation CI/CD.}
        \item{Research about new software technology.}


    \end{itemize-noindent}

}


%----------------------------------------------------------------------------------------
%   Honor and achive SECTION
%----------------------------------------------------------------------------------------

\section{Honor and Achievements}

\tabbedblock{
    \bf{2019} \> OSCP - {Offensive Security Certified Propesional} \\
    \>\+
    \textit{https://www.offensive-security.com}
}

\tabbedblock{
    \bf{2019} \> Bug Bounty Of the Years - {Top Severity in 2019} \\
    \>\+
    \textit{https://cyberarmy.id}
}



%----------------------------------------------------------------------------------------
%   CVE and achive SECTION
%----------------------------------------------------------------------------------------

\section{CVE and CWE-ID}

\tabbedblock{
    \bf{2019} \> CVE-2019-15562 - {Sql injection in Gorm (ORM golang)} \\
    \>\+
    \textit{
    Found double param injection lead to SQL-injection in find and first function.
    }\\

    \textit{https://snyk.io/vuln/SNYK-GOLANG-GITHUBCOMJINZHUGORM-543633}\\

    \textit{https://www.cvedetails.com/cve/CVE-2019-15562/}\\
  
    \textit{https://github.com/go-gorm/gorm/issues/2517}

}

%----------------------------------------------------------------------------------------
%	Project SECTION
%----------------------------------------------------------------------------------------
\section{Propesional Project Experiences}

\tabbedblock{
    \bf{2020} \> Security Assessments - {https://career.support} \\
    \>\bf{Location}\ Frisidea Tech Indonesia\\
    \>\+
    \textit{Perform penetration testing (web and mobile apps) and code review.}
}

\tabbedblock{
    \bf{2020} \> Security Assessments - {https://kenalan.app} \\
    \>\bf{Location}\ Frisidea Tech Indonesia\\
    \>\+
    \textit{Perform penetration testing (web and mobile apps) and code review.}
}

\tabbedblock{
    \bf{2018} \> Application Development - Backend \\
    \>\bf{Location}\ PwC Indonesia\\
    \>\+
    \textit{Develop application (PwC One +) that is use for PwC alumni}
}

\tabbedblock{
    \bf{2018} \> Application Development - Backend - {https://dna.danone.id} \\
    \>\bf{Location}\ Danone Indonesia\\
    \>\+
    \textit{Develop application parenrtal discussion application to discuss child nutrition.}
}

\tabbedblock{
    \bf{2017} \> Application Development - Backend - {https://ws-ahs.danone.id} \\
    \>\bf{Location}\ Aqua inc.\\
    \>\+
    \textit{Development application Aqua Home Services to order Aqua from home or office.}
}



%----------------------------------------------------------------------------------------
%	Bug bounty SECTION
%----------------------------------------------------------------------------------------

\section{Bug Bounty Experiences}

\tabbedblock{
    \bf{2019} \> Tokopedia 2019 - {https://tokopedia.com} \\
    \>\bf{Severity}\ Critical\\
    \>\+
    \textit{Find credential leaks in github like, AWS key , DB Credential, etc}
}


\tabbedblock{
    \bf{2019} \> Bukalapak 2019 - {https://bukalapak.com} \\
    \>\bf{Severity}\ Critical\\
    \>\+
    \textit{Find credential leaks in github like, AWS key , DB Credential, etc}
}


\tabbedblock{
    \bf{2019} \> Cyber Army ID Platform - {https://cyberarmy.id}\\
    \>\bf{Found}\ 1 critical and 8 high\\
    \>\+
    \textit{SSTI to RCE and ORM injection}
}



%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------
\newpage

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
    \textit{Golang} - Native\\
    \textit{Python} - Native, flask, django, japronto\\
    \textit{PHP}- Native, falcon, laravel\\
    \textit{Nodejs} - Native, express-js
}

%------------------------------------------------

\skillgroup{Web Development}
{
    \textit{HTML5, CSS3/SASS, JavaScript/CoffeeScript/jQuery}\\
    \textit{Ruby on Rails v3.1}\\
    \textit{Test:Unit, RSpec, Cucumber, Selenium} - automated testing frameworks\\
    \textit{Apache/Nginx Web Servers}\\
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
    \textit{Microsoft SQL Server 2000/2005} - database architecture and administration\\
    \textit{Transact-SQL} - data definition and manipulation\\
    \textit{SQL Profiler} - performance tuning and debugging\\
    \textit{MySQL Server}\\
    \textit{CVS, DARCS, git} - source version control\\
    \textit{ELK stack} - Elastic Search , Logstash, Kibana\\
    \textit{Nessus} 
}






%----------------------------------------------------------------------------------------
%	Open talks SECTION
%----------------------------------------------------------------------------------------

\section{Open Talks and Sharing Sessions}

\interestsgroup{
    \interest{2020 Niagahoster x Sectigo \textit{The first layer of website security.}}
    \interest{2019 Secutalks x Telkom University \textit{How to Become Security Engineer.}}
    \interest{2019 Secutalks x Telkom University \textit{How to Become Security Engineer.}}
    \interest{2019 Elastic x Tiket.com \textit{Monitoring github with ELK}}
    \interest{2019 PythonID x Tiket.com \textit{Automation Security Testing.}}
    \interest{2018 Gits Class \textit{Secure Coding Training}}
    \interest{2017 Gits Class \textit{Make Your Code Beautiful}}
}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2013-2017} \> Computer Engineering - \href{https://telkomuniversity.ac.id}{Telkom University, School Of Electrical Engineering.} \\[5pt]
\>\+
\textit{- 2015-2016 Coordinator Research Group and Study Group Laboratorium Security.}\\
\textit{- 2016-2017 Coordinator Practicums Laboratorium Security.}

}



%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------





\end{document}
